Nathan Greenslit Data Analysis Project

### 2023-02-24 code/analysis_code/dust.qmd
Proj Pt 2
- Cut out all TX Dust work- Made new Repo for that. 
- Annotated everything

Load Data that has just DUST CONC
```{r}
dust_sum<-readRDS(file = here("data", "processed_data", "dust_sum.rds")) #Dataframe with copies_mL and dust concentration for 2022
dust_0 <- readRDS(here("data", "processed_data", "dust_0.rds"))
dust_6 <- readRDS(here("data", "processed_data", "dust_6.rds"))
dust_12 <- readRDS(here("data", "processed_data", "dust_12.rds"))
dust_18 <- readRDS(here("data", "processed_data", "dust_18.rds"))

@@

New Dataframes
```{r}
#Daily Dataframe with Sum dust
daily_dust_sum<- dust_sum %>%
filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) #We do not have copies_mL for 2022-07-10

#Dataframe with just month dates
dust_month <- dust_sum %>%
  filter(date %in% as.Date(c("2022-02-16", "2022-03-09", "2022-04-20", "2022-05-11", "2022-06-14", "2022-07-07", "2022-08-09", "2022-09-13", "2022-10-18", "2022-11-15", "2022-12-13")))
```

Plot Daily Dust Conc
```{r}
dust_sum_daily<- daily_dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = dust))

@@

Plot Total Dust Conc
```{r}
dust_sum_2022<- dust_sum %>% ggplot() +geom_line(
 aes(x = date,
      y = dust),
  color = "#935d2e",
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Dust Aerosol Optical Density")+
  theme(
    axis.title.y = element_text(size = 15),
    axis.text.y = element_text(size = 10),
    axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_vline(aes(xintercept =as.Date("2022-07-07")), linetype = "dotdash", color = "4c848c")+
  geom_vline(aes(xintercept =as.Date("2022-07-19")), linetype = "dotdash", color = "4c848c")+
  scale_x_date(date_breaks = "months" , date_labels = "%b") +

#Plot Month Sample Dates over
geom_point(
  data=dust_month,
  aes(x = date,
      y = dust),
  color = "4c848c",
  size = 3,
  shape = 4,
  stroke = 1)

dust_sum_2022
```

Save as PNG
```{r}
png(file = here("results","plots", "dust_sum_daily.png"))
dust_sum_daily
dev.off()

png(file = here("results","plots", "dust_sum_2022.png"))
dust_sum_2022
dev.off()
```

>>>>

Load Data that has just dust concentrations
```{r}
dust_sum<-readRDS(file = here("data", "processed_data", "dust_conc","dust_sum.rds")) #Dataframe with copies_mL and dust concentration for 2022
#We will primary use the dust_sum data for exploratory analysis

dust_0 <- readRDS(here("data", "processed_data", "dust_conc", "dust_0.rds"))
dust_6 <- readRDS(here("data", "processed_data", "dust_conc", "dust_6.rds"))
dust_12 <- readRDS(here("data", "processed_data", "dust_conc", "dust_12.rds"))
dust_18 <- readRDS(here("data", "processed_data", "dust_conc", "dust_18.rds"))

@@

New Data frame for Daily time series 
```{r}
#Daily Dataframe with Sum dust
daily_dust_sum<- dust_sum %>%
filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) #We do not have copies_mL for 2022-07-10
```

Plot Daily Dust Concentration over Daily Time Series 
```{r}
dust_sum_daily<- daily_dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = dust))

@@

Save as PNG
```{r}
png(file = here("results","plots", "dust_sum_daily.png"))
dust_sum_daily
dev.off()
```

### 2023-02-24 code/analysis_code/dust_and_copies.qmd
Proj Pt 2
- Cut out all TX Dust work- Made new Repo for that. 
- Annotated everything

Load Data that has just DUST CONC
```{r}
#Summed Dust Concentration per day
dust_sum<-readRDS(file = here("data", "processed_data", "dust_sum.rds")) 
#Dust Conc at t = 0
#dust_0 <- readRDS(here("data", "processed_data", "dust_0.rds"))
#Dust Conc at t = 6
#dust_6 <- readRDS(here("data", "processed_data", "dust_6.rds"))
#Dust Conc at t = 12
#dust_12 <- readRDS(here("data", "processed_data", "dust_12.rds"))
#Dust Conc at t = 18
#dust_18 <- readRDS(here("data", "processed_data", "dust_18.rds"))
#Copies 
copies<- read_csv(here("data", "processed_data", "total_clean_copies.csv")) 
```

Daily Dataframe with Summed dust by day
```{r}
daily_dust_sum<- dust_sum %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) #We do not have copies_mL for 2022-07-10

@@

Plot Daily Dust Conc
```{r}
dust_fig<- daily_dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = dust),
  color = "#935d2e",
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Dust Aerosol Optical Density")+
  theme(
    axis.title.y = element_text(size = 15),
    axis.text.y = element_text(size = 10)
  )

@@

Combine Dust and Copies
```{r, fig.height = 7, fig.width= 7}
fig<- ggarrange(tot_vib, dust_fig + font("x.text", size = 10), ncol = 1, nrow = 2,align = "v")

@@

>>>>

Load Data that has just DUST CONC
```{r}
#Summed Dust Concentration per day
dust_sum<-readRDS(file = here("data", "processed_data", "dust_copies", "dust_copies_sum.rds")) 
copies<- read_csv(here("data", "processed_data", "total_clean_copies.csv")) 
```

Daily Data frame with Summed dust by day
```{r}
daily_dust_sum<- dust_sum %>%
  filter(between(date, as.Date('2022-07-07'), as.Date('2022-07-19'))) #We do not have copies_mL for 2022-07-10. No sampling occured then.

@@

Plot Daily Dust Concentration
```{r}
dust_fig<- daily_dust_sum %>% ggplot() +geom_line(
  aes(x = date,
      y = dust),
  color = "#935d2e",
  size = 1)+
  theme_bw()+
  labs(
    x = "Date",
    y = "Dust Aerosol Optical Density")+
  theme(
    axis.title.y = element_text(size = 15),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.text.x = element_text(size = 10))

@@

Combine Dust and Copies
```{r, fig.height = 4, fig.width= 4}
fig<- ggarrange(tot_vib, dust_fig + font("x.text", size = 10), ncol = 1, nrow = 2,align = "v")

@@

Save as PNG
```{r}
png(file = here("results", "plots", "vib_dust_daily.png"))
fig
dev.off()
```

### 2023-02-24 code/wrangling_code/dust_conc_processing.qmd
Proj Pt 2
- Cut out all TX Dust work- Made new Repo for that. 
- Annotated everything

---
title: "Dust Concentration"
format:
  html:
    theme: default
---
Library
```{r}
library(tidyverse)
library(here)
```

Load Data
```{r}
nrl<- read_csv(here("data","raw_data","nrl_conc.csv"))
copies<- read_csv(here("data", "processed_data", "clean_copies_date.csv"))
```

Make new dataframes  for Date and Dust for Exploratory 
```{r}
dust_tot<- nrl %>%  #Dust data for all hours
  select(dust,date,hr)

@@

dust_sum<- aggregate(dust_tot$dust, by=list(date=dust_tot$date),FUN=sum) %>% #could also use groupby
  rename("dust" = "x")
#dust_sum<- dust_sum %>%
 #left_join(dust_sum)
```

Make dataframe with Dates, Copies, and Concentration For Stats anaylsis
```{r}
copies2 <- copies %>% select(
  date, copies_mL, site)

dust_sum_copies<- dust_sum %>% left_join(copies2) #Takes df on right of pipe and joins to the df on the left of pipe

dust_t0 <- dust_0 %>% right_join(copies2)

dust_t6 <- dust_6 %>% right_join(copies2)

dust_t12<- dust_12 %>% right_join(copies2)

dust_t18<- dust_18 %>% right_join(copies2)

@@

Save Dataframes as RDS for STATS (Copies and Dust)
```{r}
saveRDS(dust_sum_copies, file = here("data", "processed_data", "dust_sum_copies.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_t0, file = here("data", "processed_data", "dust_0_copies.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_t6, file = here("data", "processed_data", "dust_6_copies.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_t12, file = here("data", "processed_data", "dust_12_copies.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_t18, file = here("data", "processed_data", "dust_18_copies.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

@@

Save Dataframes as RDS for EXPLORE (Dust)
```{r}
saveRDS(dust_sum, file = here("data", "processed_data", "dust_sum.rds")) #Dataframe with dust concentration

saveRDS(dust_0, file = here("data", "processed_data", "dust_0.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_6, file = here("data", "processed_data", "dust_6.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_12, file = here("data", "processed_data", "dust_12.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_18, file = here("data", "processed_data", "dust_18.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)
```

>>>>

---
title: "Dust Concentration"
format:
  html:
    theme: default
---
This data set is sourced from the Naval Research Lab. Aerosol optical thickness (AOT) was measures at 4 time points per day (t = 0,6,12,18).

Library
```{r}
library(tidyverse)
library(here)
```

Load Data
```{r}
nrl<- read_csv(here("data","raw_data","nrl_conc.csv")) #Dust concentration data set
copies<- read_csv(here("data", "processed_data", "total_clean_copies.csv")) #Vibrio counts data set from qPCR
```

Make new data frames for each time point as well as sum AOT per day
```{r}
dust_tot<- nrl %>%  #Dust data for all hours
  select(dust,date,hr)

@@

dust_sum<- aggregate(dust_tot$dust, by=list(date=dust_tot$date),FUN=sum) %>% #Sum of AOT by day
  rename("dust" = "x")

@@

Make dataframe with Dates, Copies/mL, and Dust Concentration For Stats analysis. Here we are combining dust data with copies/mL data. 
```{r}
#Condense copies dateset
copies2 <- copies %>% select(
  date, copies_mL, site)

#Takes df on right of pipe and joins to the df on the left of pipe 
dust_copies_sum<- dust_sum %>% left_join(copies2) #Dust at all time points
dust_copies_0 <- dust_0 %>% right_join(copies2) #T0
dust_copies_6 <- dust_6 %>% right_join(copies2) #T6
dust_copies_12<- dust_12 %>% right_join(copies2) #T12
dust_copies_18<- dust_18 %>% right_join(copies2) #T18
```

Save **dust/copies** dataframes as RDS for Stats
```{r}
saveRDS(dust_copies_sum, file = here("data", "processed_data", "dust_copies", "dust_copies_sum.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_copies_0, file = here("data", "processed_data",  "dust_copies","dust_copies_0.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_copies_6, file = here("data", "processed_data", "dust_copies", "dust_copies_6.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_copies_12, file = here("data", "processed_data",  "dust_copies","dust_copies_12.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_copies_18, file = here("data", "processed_data",  "dust_copies","dust_copies_18.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

@@

Save **Dust Concentration** data frames as RDS (good for Dust plots)
```{r}
saveRDS(dust_sum, file = here("data", "processed_data", "dust_conc", "dust_sum.rds")) #Dataframe with dust concentration

saveRDS(dust_0, file = here("data", "processed_data","dust_conc", "dust_0.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_6, file = here("data", "processed_data","dust_conc", "dust_6.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_12, file = here("data", "processed_data","dust_conc", "dust_12.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)

saveRDS(dust_18, file = here("data", "processed_data","dust_conc", "dust_18.rds")) #Dataframe with copuies_mL AND dust concentration (for stat analysis)
```

### 2023-02-24 code/wrangling_code/total_copies_calculator.qmd
Proj Pt 2
- Cut out all TX Dust work- Made new Repo for that. 
- Annotated everything

---
title: "Copies/mL"
format:
  html:
    theme: default
---
*This script takes Cq value outputs from the CFX and computes it to copies of gene targets of Vibrio*

@@

Add Dilution Column and Filter column
```{r}
dilution_daily<- site_daily %>%
  mutate(dilution = case_when(
                          Sample == "BO7"~"10",
                          Sample == "BO8"~"10",
                          Sample == "BO9"~"10",
                          Sample == "BO11"~"10",
                          Sample == "BO12"~"10",
                          Sample == "BO13"~"10",
                          Sample == "BO14"~"10",
                          Sample == "BO15"~"10",
                          Sample == "BO16REDO"~"1",
                          Sample == "BO17"~"10",
                          Sample == "BO18"~"10",
                          Sample == "BO19"~"10",
                              site  == "C2"~ "1",
                              site == "RD"~"1"), 
        dilution = as.numeric(dilution))

@@

filter_daily<- dilution_daily %>%
   mutate(filter_amt = case_when(Sample == "BO_7"~"100",
                          Sample == "BO7"~"100",
                          Sample == "BO8"~"100",
                          Sample == "BO9"~"100",
                          Sample == "BO11"~"100",
                          Sample == "BO12"~"50",
                          Sample == "BO13"~"50",
                          Sample == "BO14"~"50",
                          Sample == "BO15"~"50",
                          Sample == "BO16REDO"~"30",
                          Sample == "BO17"~"30",
                          Sample == "BO18"~"30",
                          Sample == "BO19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt))

@@

Go from CQ --> Copies/mL
```{r}
copies_daily<- filter_daily %>%
    mutate(
    log_sq = ((Cq-36.114)/-3.3844), #Equation of the line to get log(SQ)
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*10, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/2.5, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

Replace NaN with 0 for copies/mL
```{r}
replace_daily<- copies_daily %>% 
 mutate(copies_mL = ifelse(is.na(copies_mL), 0, copies_mL)) %>%
filter(!is.na(Sample))   #Dropping NAs from STD Curve

@@

Date Column
```{r}
date_daily<- replace_daily %>%
  mutate(day = substr(replace_daily$Sample,3,4)) %>% #Creates new column `day` 
  mutate(date = case_when(day == "7"~"2022-07-07", #Makes date based off of day
                          day == "7R"~"2022-07-07",
                         day ==  "8"~"2022-07-08",
                         day ==  "9"~"2022-07-09",
                         day ==  "11"~"2022-07-11",
                         day ==  "12"~"2022-07-12",
                         day ==  "13"~"2022-07-13",
                         day ==  "14"~"2022-07-14",
                         day ==  "15"~"2022-07-15",
                         day ==  "16"~"2022-07-16",
                         day ==  "17"~"2022-07-17",
                         day ==  "18"~"2022-07-18",
                         day ==  "19"~"2022-07-19")) %>%
  select(copies_mL,site,date,Type)

@@

Take the average of qPCR triplicates 
```{r}
final_daily<- date_daily %>% group_by(date,site,Type) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() #Ungroup to spit everything back out

@@

Combine Daily and Monthly 
```{r}
copies_final<- full_join(final_monthly,final_daily)
summary(copies_final)
str(copies_final)
```

Save as RDS and CSV
```{r}
saveRDS(copies_final, file= here("data","processed_data","total_clean_copies.rds"))
write.csv(copies_final,file= here("data","processed_data","total_clean_copies.csv"))

>>>>

---
title: "Copies/mL"
format:
  html:
    theme: default
---
*This script is for cleaning qPCR results on Total Vibrio enumeration. It takes Cq value outputs from the CFX (qPCR machine) and computes it to copies of gene targets of Vibrio. The data set contains a daily and monthly time series. We will be examining daily.*

@@

Add Dilution Column and Filter column. The dilution column applies if samples were diluted prior to qPCR. For example, if I diluted a sample 1:10, my dilution column would denote "10".  The filter column pertains to the amount of water sample (mL) that was concentrated onto a water filter prior to qPCR. 
```{r}
dilution_daily<- site_daily %>%
  mutate(dilution = case_when(
                          Sample == "BO7"~"10", #BO site was diluted 1:10
                          Sample == "BO8"~"10",
                          Sample == "BO9"~"10",
                          Sample == "BO11"~"10",
                          Sample == "BO12"~"10",
                          Sample == "BO13"~"10",
                          Sample == "BO14"~"10",
                          Sample == "BO15"~"10",
                          Sample == "BO16REDO"~"1",
                          Sample == "BO17"~"10",
                          Sample == "BO18"~"10",
                          Sample == "BO19"~"10",
                              site  == "C2"~ "1", #Canals and Gulf were not diluted
                              site == "RD"~"1"), 
        dilution = as.numeric(dilution))

@@

filter_daily<- dilution_daily %>%
   mutate(filter_amt = case_when(Sample == "BO_7"~"100", #100mL concnetrated onto filter
                          Sample == "BO7"~"100",
                          Sample == "BO8"~"100",
                          Sample == "BO9"~"100",
                          Sample == "BO11"~"100",
                          Sample == "BO12"~"50",
                          Sample == "BO13"~"50",
                          Sample == "BO14"~"50",
                          Sample == "BO15"~"50",
                          Sample == "BO16REDO"~"30", #30 mL concentrated onto filter 
                          Sample == "BO17"~"30",
                          Sample == "BO18"~"30",
                          Sample == "BO19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt))

@@

Go from CQ --> Copies/mL
```{r}
copies_daily<- filter_daily %>%
    mutate(
    log_sq = ((Cq-36.114)/-3.3844), #Equation of the line to get log(SQ):  This comes from running a standard curve during qPCR. 
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*10, #SQ*Reaction Volume: Each qPCR reaction was 10µL
    copies_uL_1_10 = copies_rxn/2.5, #Copies/RXN / DNA Template Volume: Each 10µL reaction had 2.5µL of DNA added. 
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

Some samples did not amplify: Replace NaN with 0 for copies/mL
```{r}
replace_daily<- copies_daily %>% 
 mutate(copies_mL = ifelse(is.na(copies_mL), 0, copies_mL)) %>%
filter(!is.na(Sample))   #Dropping NAs from STD Curve

@@

Date Column: This adds a date correpsonding the a number in the sample name. 
```{r}
date_daily<- replace_daily %>%
  mutate(day = substr(replace_daily$Sample,3,4)) %>% #Creates new column `day` 
  mutate(date = case_when(day == "7"~"2022-07-07", #Makes date based off of day
                          day == "7R"~"2022-07-07",
                         day ==  "8"~"2022-07-08",
                         day ==  "9"~"2022-07-09",
                         day ==  "11"~"2022-07-11",
                         day ==  "12"~"2022-07-12",
                         day ==  "13"~"2022-07-13",
                         day ==  "14"~"2022-07-14",
                         day ==  "15"~"2022-07-15",
                         day ==  "16"~"2022-07-16",
                         day ==  "17"~"2022-07-17",
                         day ==  "18"~"2022-07-18",
                         day ==  "19"~"2022-07-19")) %>%
  select(copies_mL,site,date,Type)

@@

Each sample (Date) was done in triplicate for qPCR: We need to take the average of qPCR triplicates 
```{r}
final_daily<- date_daily %>% group_by(date,site,Type) %>% #Group all chr together. All that should be left out is the numeric vector we want to work with (in this case, copies_mL)
  summarize_if(is.numeric, mean) %>%
  ungroup() #Ungroup to spit everything back out

@@

Combine Daily and Monthly data sets back togthether. 
```{r}
copies_final<- full_join(final_monthly,final_daily)
summary(copies_final)
str(copies_final)
```

Save as RDS and CSV
```{r}
#saveRDS(copies_final, file= here("data","processed_data","total_clean_copies.rds"))
write.csv(copies_final,file= here("data","processed_data","total_clean_copies.csv"))

### 2023-02-24 products/manuscript/Manuscript.qmd
Proj Pt 2
- Cut out all TX Dust work- Made new Repo for that. 
- Annotated everything

---
title: "Nathan Greenslit Data Analysis Project"
subtitle: ""
author: Andreas Handel
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../dataanalysis_template_references.bib
csl: ../apa.csl
---

This uses MS Word as output format. [See here](https://quarto.org/docs/output-formats/ms-word.html) for more information. You can switch to other formats, like html or pdf. See [the Quarto documentation](https://quarto.org/) for other formats.

@@

# Summary/Abstract
_Write a summary of your project._

@@

## Description of data and data source

@@

To cite other work (important everywhere, but likely happens first in introduction), make sure your references are in the bibtex file specified in the YAML header above (here `dataanalysis_template_references.bib`) and have the right bibtex key. Then you can include like this:

@@

_Describe your methods. That should describe the data, the cleaning processes, and the analysis approaches. You might want to provide a shorter description here and all the details in the supplement._

## Data aquisition
_As applicable, explain where and how you got the data. If you directly import the data from an online source, you can combine this section with the next._

## Data import and cleaning
_Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along._

## Statistical analysis
_Explain anything related to your statistical analyses._

@@

_Use a combination of text/tables/figures to explore and describe your data. Show the most important descriptive results here. Additional ones should go in the supplement. Even more can be in the R and Quarto files that are part of your project._

@tbl-summarytable shows a summary of the data.

Note the loading of the data providing a **relative** path using the `../../` notation. (Two dots means a folder up). You never want to specify an **absolute** path like `C:\ahandel\myproject\results\` because if you share this with someone, it won't work for them since they don't have that path. You can also use the `here` R package to create paths. See examples of that below.

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable)
```

@@

_To get some further insight into your data, if reasonable you could compute simple statistics (e.g. simple models with 1 predictor) to look for associations between your outcome(s) and each individual predictor variable. Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by sex."
#| echo: FALSE
knitr::include_graphics(here("results","height_weight_stratified.png"))
```

@@

_Use one or several suitable statistical/machine learning methods to analyze your data and to produce meaningful figures, tables, etc. This might again be code that is best placed in one or several separate R scripts that need to be well documented. You want the code to produce figures and data ready for display as tables, and save those. Then you load them here._

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","resulttable2.rds"))
knitr::kable(resulttable2)
```

@@

## Summary and Interpretation
_Summarize what you did, what you found and what it means._

## Strengths and Limitations
_Discuss what you perceive as strengths and limitations of your analysis._

## Conclusions
_What are the main take-home messages?_

_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_

This paper [@leek2015] discusses types of analyses.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header. Many more style files for almost any journal [are available](https://www.zotero.org/styles). You also specify the location of your bibtex reference file in the YAML. You can call your reference file anything you like, I just used the generic word `references.bib` but giving it a more descriptive name is probably better.

>>>>

---
title: "Nathan Greenslit Data Analysis Project"
subtitle: ""
author: Nathan Greenslit
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
---

@@

# Summary/Abstract

@@

@@

@@

## Data aquisition

## Data import and cleaning

This project works with three primary data sets. (1) Enumeration of Vibrio bacteria as copies/mL from quantitative PCR (copies_master.csv), (2) Dust concentrations as aerosol optical thickness (AOT) derived from the Naval Research Lab (nrl_conc.csv), and (3) Temperature and Salinity across the daily time series (ysi\_.csv). Below is a brief summary of how each data set was cleaned. More details can be found in the supplementary files, containing the code and comments describing what each line does. Please refer to the `project_README.md` file located in the NathanGreenslit-MADA-Project folder for details on the repository contents and  instructions on reproducibility

### Cleaning of Total Vibrio Enumerations Data set

Quantitative PCR provides enumeration results as "cycle threshold or Cq" values. This depicts the cycle number in which enough of the DNA target was detectable to be amplified. Lower Cq values correspond to higher target concentrations (as it takes less cycles to amplify), and vice verse for higher Cq values. The cleaning of this data set consisted of converting these Cq values into something that can be used to quantify Vibrio (copies of target per mL of seawater). To do so, I needed to take into account the amount of water sample that was concentrated on a filter, the total amount of DNA that was eluted following a DNA extraction, and the amount of DNA template added to each mix for qPCR (to name a few). Taking these into account, we are able to calculate our way from Cq values to copies of Vibrio per mL of seawater. qPCR was conducted in triplicate, so the last step was to take the average of the three replicates to have a final value per sample. A date column was also added for each sample.

### Cleaning of Dust Concentration (AOT) Data set

Dust concentration (AOT) was collected at time points 0 hour, 6 hour, 12 hour, and 18 hour. In this script, I made different data sets based on time points as well as a data set containing the summed dust concentration (of all time points) per day. For downstream statistical analysis, it will be helpful to have these different data sets to compare to time of sample collection.

### Cleaning of Temperature and Salinity Data set

This data set did not require any cleaning.

@@

### Dust

![](images/dust_sum_daily.png)

This figure depicts the summed dust concentration (time points 0hr-18hr) across the daily time series. During the time series, two small period of higher dust AOT occurred on the 9th and 13th respectively. A much larger spike in AOT was observed on the 16th.

### Daily Vibrio

![](images/vib_dust_daily.png)

The top portion of the figure depicts total enumerated Vibrio as copies per mL, with color by site. There is a noticeable shift in copies in the Gulf site, a less noticeable but still present shift in Blind Oso Bay, and practically no changes in the Canal site. The bottom portion of the figure depicts the dust concentration (AOT) across the daily time series. Initial shift in copies per mL at the Guld and Blind Oso occur around initial dust introduction on the 13th, and experience another shift around the time of higher dust input on the 16th.

### Temperature and Salinity

![](images/temp_sal.png)

Temperature and salinity at the Canal site is relatively high and consistent as compared to the other sites. Blind Oso Bay experiences some shifts in temperatures and drastic fluctuations in salinity. The Gulf site had a drop in temperature (possibly due to upwelling) and relatively consistent ocean salinities

@@

@@

@@

## Summary and Interpretation

## Strengths and Limitations

## Conclusions
